### 2021-05-04 docs/manuscript/PLOS-MSc-Thesis.tex
Improve Fig5 caption
- Add that black circles are as in Fig3
- Add that colors represent clusters.

\begin{figure}
 \includegraphics[width=\textwidth]{figures/results/Fig5}
 \caption{\bf Network of topologies separated by two mutational steps.}
 The network shows that all the topologies are connected by two or less
 mutational steps, except for topology number 420 (big red circle). Big black
 circles correspond to the 15 topologies with higher abundance.
 \label{fig:2neut-net}
\end{figure}

>>>>

\begin{figure}
 \includegraphics[width=\textwidth]{figures/results/Fig5}
 \caption{\bf Network of topologies separated by two mutational steps.}
 The network shows that almost all the topologies are connected by two or less
 mutational steps. Big red circle represents topology 420 that remains
 unconnected from the main graph. Big black circles correspond to the 15
 most abundant topologies described in Fig~\ref{fig:neutral-network}.
 Different colors in the graph represent different clusters of topologies.
 \label{fig:2neut-net}
\end{figure}
